### 2019-03-26 README.Rmd
update readme

[![Build Status](https://api.travis-ci.org/dynverse/dynbenchmark.svg)](https://travis-ci.org/dynverse/dynbenchmark)
![Lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg) <a href = "package/man/figures/logo.svg"><img src="package/man/figures/logo.png" align="right" /></a> [![doi](https://zenodo.org/badge/doi/10.1101/276907.svg)](https://doi.org/10.1101/276907)

@@

*Note that this preprint is currently **very** outdated. An updated manuscript will be published soon, you can browse below for more recent results*

>>>>

[![Build Status](https://api.travis-ci.org/dynverse/dynbenchmark.svg)](https://travis-ci.org/dynverse/dynbenchmark)
![Lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg) <a href = "package/man/figures/logo.svg"><img src="package/man/figures/logo2.png" align="right" width="125" height="144"/></a> [![doi](https://zenodo.org/badge/doi/10.1101/276907.svg)](https://doi.org/10.1101/276907)

@@

## Dynverse

Under the hood, dynbenchmark makes use of most dynverse package for running the methods, comparing them to a gold standard, and plotting the output. Check out **[dynverse.org](https://dynverse.org)** for an overview!
